Network Configuration Synthesis with Abstract Topologies \vspace{1cm}

### 2017-04-15 paper/abstraction/paper.tex
remove some old comments and change graph positions to look better

%% publication rights
%\setcopyright{acmcopyright}
\setcopyright{acmlicensed}  % default
%\setcopyright{rightsretained}

@@

%\author{Paper \#324, 14 pages}

%\authorinfo{Ryan Beckett}{Princeton University}{rbeckett@cs.princeton.edu}
%\authorinfo{Ratul Mahajan}{Microsoft Research}{ratul@microsoft.com}
%\authorinfo{Todd Millstein}{UCLA}{todd@cs.ucla.edu}
%\authorinfo{Jitendra Padhye}{Microsoft Research}{jpadhye@microsoft.com} 
%\authorinfo{David Walker}{Princeton University}{dpw@cs.princeton.edu}

%\numberofauthors{1}

@@

% Hence, one approach to improving network reliability is to develop better
% languages for network configuration.  Such languages should be defined at a
% higher level of abstraction than existing configuration languages and provide
% support built-in support for verification of important properties, thereby
% avoiding entire classes of configuration errors automatically.

%An important class of networks are the large \emph{structured networks}
%commonly deployed in industrial data centers.

@@

%It is no wonder that a major
%network outage, such as the one that grounded all United Air flights
%in July 2015~\cite{x}, makes international news every few months.

@@

To address the challenge of configuration synthesis in the presence of abstract roles, we develop \sysname. 
%BGP, unlike link state protocols
%such as OSPF, is also particularly
%useful in our setting because it contains features that help us localize the effects of changes.
\sysname
allows operators to input \emph{abstract topologies} in terms of roles
and their connectivity. For instance, they may specify roles for ``top-of-rack''
and ``aggregation" routers and specify that every top-of-rack router connects to
at least two aggregation routers (to tolerate the failure of a link to an
aggregation router). \sysname takes two additional inputs. 
The first is a  high-level specification of routing policy, for which we borrow notation from the original
\Propane system~\cite{propane}.  While \Propane policies refer to concrete devices,
\sysname policies refer to abstract roles.
The final input to \sysname is the fault-tolerance requirements of the network, such as the number of simultaneous link failures it can tolerate without loss of connectivity for any traffic flow.

Based on these inputs, \sysname generates one template per role. 
These templates specify routing policy using BGP (border gateway protocol). 
BGP is the standard protocol for interdomain routing and is also commonly used within data centers because of its scalability and support for rich policies.\footnote{However, BGP is not the only routing protocol used in existing networks. In the future, we will extend our work to  other protocols such as OSPF.}
%
Our templates are correct for {\em any} concrete topology that complies with the abstract topology. They are also evolution friendly. 
When the network evolves from one compliant concrete topology to another, only the configurations of devices that acquire or lose a neighbor need to change. 
This guarantee is the best that any system can give as neighbor relationships are explicitly 
configured in devices.  We achieve it in part by leveraging BGP features that allow arbitrary tags on routing announcements and expressing policy using such tags (instead of router identifiers). 
%These features makes it possible to change network topologies without reflecting those changes in the configurations of distant routers.  
%Other control plane protocols that do not provide such tagging mechanisms or that implement link-state protocols as opposed to path-vector protocols would not be able to avail themselves of these techniques.
%No other device in the network is impacted.

During synthesis, our compiler analyzes abstract topologies to determine
the fault tolerance properties of the specified routing policy.  This analysis yields a lower  
bound on the number of link failures required to disconnect one abstract location from another. 
%given the connectivity constraints of the abstract topology. 
Any concrete instance of the abstract topology will adhere to the given fault tolerance property.

@@

\vspace{0.5em}
\noindent
\textbf{Contributions}: To summarize, our contributions are:
%
\begin{itemize}[noitemsep,nolistsep,label={\large\textbullet}]
\item New topology abstractions for network programming
based on graph homomorphisms and connectivity rules.
\item New algorithms for analyzing routing policy and fault tolerance over
abstract topologies.
%one which guarantees correct compilation and one which determines fault tolerance
%properties of network policy.
%Both algorithms provide guarantees for any
%concrete network satisfying the abstract connectivity invariants.
%\item Design of a template generation strategy that supports network
%evolution.
\item Implementation and evaluation of a \sysname compiler that generates
BGP templates and is much faster
than compilers based on concrete topologies.
\end{itemize}

%% Indeed, over the last several years, many researchers have begun to
%% develop such languages~\cite{frenetic,pyretic,pane,nettle,netkat}.
%% However, the bulk of this research has targeted software-defined
%% networks (SDN), a new networking technology that has emerged over the last
%% decade.  Unfortunately, the vast majority of today's networks
%% continue to use traditional networking techology---upgrading to SDN is
%% expensive and technically challenging.

%% In a traditional network, every router runs an independent instance of
%% a distributed protocol that
%% exchange messages about available routes to destination addresses.
%% Each router is configured independently, but the overall behavior
%% of the network---the paths from one server to another, for instance---depend
%% upon the

@@

All route announcements carry an {\em AS path}, the sequence of BGP networks, called autonomous systems (ASes), that will be traversed to reach the destination.
%When BGP is used inside a data center, each router tends to be its own AS.
Optionally, they may also include one or more {\em communities}, which are arbitrary tags whose semantics are agreed upon out of band.

@@

To simplify them, operators are adopting a template-based approach~\cite{hatch,thwack}. Instead of authoring a configuration per router, operators author a template per role.
%
A {\em role} is a specific function that is served by one or more routers.
%\footnote{If a role is played by devices from multiple vendors, there is one template per role-vendor combination because templates use vendor configuration languages.}
%
For example, the network in Figure~\ref{fig:example} might have five roles: spine, global aggregator, global ToR, local aggregator, and local ToR.
%
Figure~\ref{fig:templates} shows an example of what a small component of a template for the spine role in the two data centers might look like. The template has parameters for various aspects of the configuration (\EG, neighbor list, local prefixes) and is compiled to low-level device configurations by instantiating the parameters using the network topology and a database of network information.

@@

%Unfotunately, currently, there is no way to predict which variations will behave correctly for a given set of templates.

@@

%\subsection{Inputs}

@@

%Ideally, we would like to find a suitable topology abstraction that can describe both of the data centers from figures~\ref{fig:example} and~\ref{fig:example2} as well as any reasonable generalization of these data centers. \sysname provides several abstraction mechanisms to achieve this goal.

%We introduce our topology abstractions using the networks from \S\ref{sec:motivation}.
Our topology abstractions consist of several concepts.
The primary one is a role-based abstraction that allows an operator to map routers in the concrete network to roles in the abstract network. Figure~\ref{fig:example3} shows an example of this abstraction for both networks from \S\ref{sec:motivation}. In the example, the concrete networks are abstracted into a new topology with 5 different roles: local ToR (TL), global ToR (TG), local aggregator (AL), global aggregator (AG), and spine (S).

@@

On its own, this abstraction loses a lot of information about the concrete network's structure, making it difficult to reason precisely about fault-tolerance.
%which would hinder a useful analysis of its fault-tolerance.
For example, with this abstraction any spine router may or may not connect to any aggregator router.
%
To capture concrete networks more precisely,
we introduce additional concepts. The first is topology hierarchy, captured by P and Q, which indicate that nodes in the ToR and aggregator roles are grouped into pods.
The second is node and edge \emph{multiplicity}. Each edge (and node) is labelled
with a symbolic variable (\EG, $e1$) that denotes a constraint on the number of edges (and nodes) that may appear in any valid concrete network. Operators can capture concrete network invariants by adding constraints on the symbolic variables using logical formulas.

@@

Our topology abstractions can also capture concrete topologies by using a one-to-one correspondence between abstract and concrete nodes/edges. This allows operators to define complex networks in which some (e.g., legacy) parts of the network cannot evolve while others can.
%It also means that our compiler subsumes those that operate only over concrete topologies.

@@

Second, \sysname checks if the fault-tolerance policy can be met by considering the joint impact of the abstract topology and routing policy. Joint analysis is needed, because connectivity depends on both: traffic will not flow along valid topological paths if the routing policy disallows it.
%
We develop a sound analysis based on computing the minimum
number of edge-disjoint, policy-compliant paths between pairs of nodes
over abstract topologies. If this number is less
than the desired fault-tolerance level for a pair of nodes, \sysname declares that the
policy cannot be met.
%\ryan{Possibly cut here}
%More specifically,
%for each abstract role in the network, our analysis will learn facts about the
%number of disjoint paths to routers in that role.  For example,
%the fact $A_{S}(2,3)$ states that for \emph{all} groups of 2 nodes
%in the $S$ (Spine) role, there are 6 disjoint paths to the group---3
%for each of the 2 nodes. A fact such as $S_{S}(2,3)$, states that
%\emph{some} group of 2 nodes has the property as opposed to all.
%More generally, there is one quantifier ($A$ for all groups
%and $S$ for exists a group).  When nodes are nested within pods,
%there is one quantifier for each level of the hierarchy, so
%$S_P S_{TG} (i,j)$ means that for some pod from the $P$ group of pods
%and for some nodes in the $TG$ role within that pod, there exists a
%group of $i$ nodes with $j$ paths to each node in the group.

%\ryan{Possibly cut here}
%As an example, suppose we want to compute the number of of disjoint paths between any global ToR and spine router in Figure~\ref{fig:example3}.
%The analysis begins with the fact
%$S_P S_{TG} (1,1)$---there is some group of
%nodes of size 1 in the $TG$ role in some pod $P$ such that any initial
%node in the $TG$ role has 1 disjoint path to it (and all such paths are
%edge-disjoint). Since the abstract topology specifies that each node in
%the $TG$ role is in
%a full mesh with nodes in the $AG$ role within any given pod, we
%infer the fact $S_P A_{AG}(e1,1)$. This says that
%any group of nodes of size e1 in the $AG$ role is reachable with at
%least 1 path to each such node from any initial node in
%the $TG$ role.
%
%After one more step, the analysis will learn a fact of the form $A_{S}(1,1)$, which means that any single spine node is reachable via a single disjoint path from any initial global ToR node
%In fact, due the valley-free routing constraint, a single path is
%the worst-case fault-tolerance level for the concrete network from
%Figure~\ref{fig:example2}.

@@

%
%The constraint prevents traffic from over taking a path that traverses
%either [Agg->Tor->Agg] or [Spn->Agg->Spn]. The final policy remains the same as before,
%by combining each of these policies together.
%
%

@@

%For example, the combining the Routing and Local constraints in the data center policy from \S\ref{sec:overview} would result in the following \sysname policy:
%
%\begin{code}
%\$PG  \Path \End(TG),
%\$PL  \Path \End(TL) \ensuremath{\cap} \Always(\In),
%\True \Path \Exit(Peer1) \Prefer \Exit(Peer2)
%\end{code}
%\noindent%
%

%After converting the routing policy to the regular expression based language,
We are now ready to generate the PG. Intuitively, the PG captures topology and routing constraints by ``intersecting" the finite automata associated with the policy regular expressions with the graph structure of the topology.
%The PG compactly encodes all paths that protocol messages should be passed along through the network in order to guarantee that the BGP-speaking devices find policy-compliant paths dynamically.
%
%Although \sysname policies describe the routes that traffic should take through the network, network protocols (including BGP) typically disseminate router information in the opposite direction. For example, a router Y will tell its neighbor X that it has a route to the destination meaning that X can send traffic through Y. For this reason, we start by compiling
%
Because there can be a separate routing policy for each predicate $t$ in the policy, we construct one PG for each predicate.

@@

Figure~\ref{fig:example-compilation} shows the PG for the data center policy that applies to all external traffic ($\CD{\True \Path \Exit(N1~\Prefer~N2)}$).
%
%\begin{code}
%\True \Path \Exit(\sf{Peer1}) \Prefer \Exit(\sf{Peer2})
%\end{code}
%\noindent%
%
The first automaton represents the more preferred constraint $\CD{\Exit(N1)}$ and the second automaton represents the less preferred constraint $\CD{\Exit(N2)}$. The PG is shown for both an instance of a simple concrete network matching the abstraction from \S\ref{sec:overview} as well as for the abstract topology.

@@

\begin{lem}
\label{lem:homomorphism}
If we have a graph homomorphism $f : G \rightarrow G^A$, concrete product graph $PG = (G',\mathit{start},\Pref)$ and abstract product graph $PG^A = (G'^A, \mathit{start}^A, \Pref^A)$, then there is a homomorphism $f_{pg} : G' \rightarrow G'^A$ where:
\[ \begin{array}{rcl}
  f_{pg}( \mathit{start} ) & = & \mathit{start}^A  \\
  f_{pg}( (l,q_1,\ldots,q_n) ) & = & (f(l),q_1,\ldots,q_n) \\
\end{array} \]
\end{lem}
%
As shown in \S\ref{sec:generation}, our generation strategy commutes with template instantiation, meaning that we obtain the same results if we instantiate the abstraction early, or if we defer the instantiation until after template generation.
%
%Lemma~\ref{lem:homomorphism} provides intuition as to why our strategy for generating templates is correct.
%Abstract product graphs are related to concrete product graphs via a graph homomorphism, just as abstract topologies are related to concrete topologies via a graph homomorphism.

@@

%In practice, operators would often like to reason about a variety of properties for, not only their current network topology, but also future versions of it.
%% The Product Graph provides a convenient representation to capture the joint impact of both topology and routing policy. In this section we present an analysis that operates over the abstract Product Graph to find a lower bound on the number of disjoint paths between pairs of concrete nodes. Answering questions about the number of disjoint paths between nodes allows operators to reason about many useful network properties such as reachability (\IE, is there at least one path) and fault tolerance (\EG, how many failures will disconnect certain routers).

%\subsection{Abstract k-disjoint paths}
%\label{sec:property-checking}

@@

%The problem for \sysname is harder because it must verify that all possible concrete instantiations of an abstract topology satisfy the fault-tolerance policy, which requires a fundamentally different approach.

%
We frame satisfying the fault-tolerance requirements as an analysis problem over the structure of the PG. In particular, we develop an analysis that uses information embedded in the abstract topology to infer bounds on the number of edge-disjoint paths between pairs of concrete nodes.

%
For each node in the abstract PG,
the idea is to infer facts learned about the number of edge-disjoint paths
to groups of concrete routers in the node's role.
More specifically, we maintain fact of the form:
%
\[ \begin{array}{c}
  L_{X_1}, \ldots, L_{X_n}(j,k)
\end{array} \]
\noindent
%
where each label $L \in \{S,A\}$ is either $S$, which stands for ``some" or is $A$, which stands for ``all". There is one label for each pod in the abstraction pod hierarchy under which the abstract node appears. For a given node, $L_{X_1}$ corresponds to the outermost pod, $L_{X_{n-1}}$ corresponds to the innermost pod, and $L_{X_n}$ to the node itself.
Semantically, $L_{X_1}, \ldots, L_{X_n}(j,k)$ means that starting from some concrete source node, for some/all pods $X_1, \ldots, X_{n-1}$
and for some/all groups of nodes in the role $X_n$ of size $j$,
%, $L_{X_2}, \ldots, L_{X_n}(j,k)$ holds. The base case $L_{X_n}(j,k)$ means that for "some"/``all" groups of size $j$ concrete routers,
there are $k$ paths to each such that all $j*k$ paths are edge-disjoint.

@@

Figure~\ref{fig:inference-rules} displays the collection of rules used to infer facts about disjoint paths.
Each rule is read from bottom to top. The label on the bottom left is a known fact. We use $L$ to represent a rule that is parametric over the label ($S$ or $A$). Labels on other nodes correspond to facts learned after applying the rule. The box shows the conditions that must be valid, given the abstraction constraints, for the rule to apply. 
%Validity ensures that the condition holds for all concrete instantiations of the topology.

@@

The first rule, \infrule{I-out1} applies to a learned fact of the form $L_m(j,k)$ where the number of outgoing edges from any concrete node in the $m$ role is greater than 0. In the worst case, the largest group of concrete nodes we could hope to reach at the $n$ role would be $e_1$ since all j nodes at the bottom may have outgoing edges to the same concrete nodes at the top. Furthermore, the total number of disjoint paths to the $j$ nodes at the bottom is equal to $j*k$. Since extending the existing disjoint paths with disjoint edges keeps the paths disjoint, and since we cannot exceed the current number of disjoint paths to the concrete nodes in role $m$ on the bottom, the largest reachable group for the role $n$ on the top will be $min(j*k,e_1)$.
%
We conservatively use $1$ for the number of disjoint paths to each node in role $n$, since when $n$ is very large, all reachable nodes in role $m$ might only have a single edge to completely different nodes in $n$.
%However, because we do not know for certain that all $j$ nodes in role $m$ have outgoing edges to the same nodes at the top, we conservatively use $1$ for the number of disjoint paths to each node on top.
%For example, if $n$ is very large, then each node in role $m$ may have only a single edge to each reachable node in role $n$.

@@

%The rule \infrule{I-out2} follows a similar line of reasoning. It says that if any group of size $j$ with $k$ disjoint paths to each is reachable in the bottom role, and there is at least one incoming edge for each concrete node in the top role, then there are $min(j,e_2)$ disjoint paths to any single concrete node in the top role. This is because we can choose the $j$ nodes on the bottom for which we want to find disjoint paths, and then use each of the $e_2$ disjoint incoming edges for the particular node at the top connecting it to the bottom.

@@

%The rule \infrule{I-mincut} can be thought of as an assertion about the fault tolerance between nodes in two roles. The rule applies to an edge that has been annotated with a $mincut(X)$ statement, which means that there are at least $X$ disjoint paths between any node in role $m$ and any node in role $n$.

@@

%The algorithm associates with each inference, the set of abstract locations used to derive the inference, \IE, an overapproximation of set of concrete locations used for the edge-disjoint paths. When applying an inference rule between an invariant at role $m$, with a set of abstract locations $C$, to learn an invariant at role $n$, we associate the new invariant with the set $C \cup \{ n \}$.
%
%When, at a single PG node there is an inference $L_{X_1} \dots L_{X_{n-1}}$ A$_m(j,k)$ with location set $C$ and inference $L_{X_1} \dots L_{X_{n-1}}$ L$_m(j',k')$ with location set $D$, where $C \cap D = \emptyset$, we add a new inference with location set $C \cup D$:
%
%$$L_{X_1} \dots L_{X_{n-1}} L_m(\min(j, j'), k + k')$$
%
%\noindent
%The idea is that, because non-overlapping abstract paths can never contain overlapping concrete paths, due to the graph homomorphism property, we can merge inferences about these disjoint paths in the abstraction.

@@

The algorithm could infer that there is at least 1 disjoint path to any spine router, and at least 2 disjoint paths to any TL router. In this case, the analysis is precise. There exists a concrete network, namely the data center from Figure~\ref{fig:example2}, where a single failure can disconnect a global ToR from a spine router due to the valley-free constraint.
%The bound on the fault tolerance between ToR and spine routers can also be used to determine that an aggregation-induced black hole may arise at the data center boundary after a single failure in some concrete instantiation.

@@

  %\hrulefill%

@@

%
For example, in Figure~\ref{fig:example-compilation} the inequality $(S1,0,1) \leq (S1,1,0)$ holds since nodes on the left side of the PG can always match transitions made on the right hand side with respect to the $\geq_{rank}$ relation. This relation does not hold the other way around since $(S1,0,1) \ngeq_{rank} (S1,1,0)$. Therefore, advertisements received at $S1$ with tag $(1,0)$ must be preferred to those received at $S1$ with tag $(0,1)$.
%
Notice that in the abstract PG $(S,0,1) \leq (S,1,0)$ also holds. This leads to the following observation:

@@

To prevent the non-local changes induced by template variables, we modify compilation in the following ways. First, we associate a new unique community tag for each template variable (\EG, {\small \$GP}), and add this tag where the route is originated (\EG, role TG). Then, template variable tests elsewhere in the policy are replaced with a new test on this tag. Finally, during template instantiation the tags are left unmodified.
%Therefore, we can prevent modifications to the spine routers' configurations by associating a new unique community tag for template variable {\small \$GP} and then replacing each match on {\small \$GP} with a test on the new community tag. The new ToR must now simply attach the new community tag to advertisements for its prefixes so downstream routers can match against it. 
Figure~\ref{fig:bgp-configs} (right) shows the spine and ToR templates after this transformation. Routers in the TG role will originate ($\{ \mathrm{start} \}$) global prefixes and tag them with a unique tag, while routers in the spine role match the tag.

@@

      Fat tree~\cite{fattree} & -- & \cmark & \cmark & \cmark & \cmark  \\ \hline
      Facebook~\cite{facebook-fattree} & -- & \cmark & \cmark & \cmark & \cmark \\ \hline
      F10~\cite{f10-fattree} & -- & \cmark & \cmark & \cmark & \cmark \\ \hline
      VL2~\cite{vl2-fattree} & -- & \cmark & \cmark & \cmark & \cmark \\ \hline
%      \end{tabular}
%  \end{center}
%  \vspace{-.6em}
%  \caption{Expressiveness and analysis precision for fat tree topologies with valley-free routing policy.}
%  \label{fig:analysis-precision2}
%\end{figure}
%
%\begin{figure}[t!]
%  \begin{center}
%      \begin{tabular}{| l | c | c | c | c | c | }
%      \hline
%      \textbf{Topology} & \textbf{Fixed} & \multicolumn{2}{|c|}{\textbf{Reachability}} & \multicolumn{2}{|c|}{\textbf{K-paths}} \\ \hline
%      & & Some & All & Some & All \\
%      & & Pairs & Pairs & Pairs & Pairs \\ \hline

@@

%For each topology in Figure~\ref{fig:analysis-precision} we define a suitable abstraction. Since many topologies have tunable parameters (\EG, the recursion depth $k$ for the DCell topology), we list all such parameters that are fixed for the abstraction. For all topologies (Figure~\ref{fig:analysis-precision}), we implement a shortest path routing policy. Additionally, for clos-style topologies, we implement a valley-free routing policy (Figure~\ref{fig:analysis-precision2}) for comparison. In each case, we record the precision of the analysis in terms of whether or not it is able to accurately prove reachability and/or the correct number of disjoint paths between some or all pairs of nodes from a fixed source.

%\para{Fat Tree Topologies}
%
%The fat tree topology is a widely used data center topology. We look at the precision of our analysis on four fat tree variants used in practice: a standard fat tree~\cite{fattree}, the Facebook fat tree~\cite{facebook-fattree}, the F10 fault tolerant fat tree~\cite{f10-fattree}, and the VL2 topology~\cite{vl2-fattree}. For each fat tree variant, we use a tiered abstraction similar to that in our previous example. Each fat tree topology is parameterized over the number of pods $k$, which can be scaled up in the abstraction to allow for expansion.

@@

\para{Hypercube Topologies}
Hypercube variants can be used as an alternative to Clos-style topologies for networks with port density routers. The HyperX~\cite{hyperx} topology generalizes the hypercube and butterfly topologies and includes parameters $L$ for the lattice dimension of the network, and $S_i$ for the node multiplicity of each dimension $i$.
%$K_i$ for the bandwidth of links for each dimension,
%and $T$ for the number of terminal nodes (servers) connected to each router.
For a fixed number of dimensions $L$, we abstract each full mesh of $S_L$ nodes into its own abstract node. Nodes in dimension $S_{x-1}$ are abstracted using pods of abstract nodes from dimension $S_x$. Figure~\ref{fig:example-abstractions} shows an example for $L=2$.
%For all hypercube variants, the fault-tolerance analysis is precise.

>>>>

%% publication rights
%\setcopyright{acmcopyright}
\setcopyright{acmlicensed}
%\setcopyright{rightsretained}

@@

@@

@@

@@

To address the challenge of configuration synthesis in the presence of abstract roles, we develop \sysname. 
\sysname
allows operators to input \emph{abstract topologies} in terms of roles
and their connectivity. For instance, they may specify roles for ``top-of-rack''
and ``aggregation" routers and specify that every top-of-rack router connects to
at least two aggregation routers (to tolerate the failure of a link to an
aggregation router). \sysname takes two additional inputs. 
The first is a  high-level specification of routing policy, for which we borrow notation from the original
\Propane system~\cite{propane}.  While \Propane policies refer to concrete devices,
\sysname policies refer to abstract roles.
The final input to \sysname is the fault-tolerance requirements of the network, such as the number of simultaneous link failures it can tolerate without loss of connectivity for any traffic flow.

Based on these inputs, \sysname generates one template per role. 
These templates specify routing policy using BGP (border gateway protocol). 
BGP is the standard protocol for interdomain routing and is also commonly used within data centers because of its scalability and support for rich policies.\footnote{However, BGP is not the only routing protocol used in existing networks. In the future, we will extend our work to  other protocols such as OSPF.}
%
Our templates are correct for {\em any} concrete topology that complies with the abstract topology. They are also evolution friendly. 
When the network evolves from one compliant concrete topology to another, only the configurations of devices that acquire or lose a neighbor need to change. 
This guarantee is the best that any system can give as neighbor relationships are explicitly 
configured in devices.  We achieve it in part by leveraging BGP features that allow arbitrary tags on routing announcements and expressing policy using such tags (instead of router identifiers).

During synthesis, our compiler analyzes abstract topologies to determine
the fault tolerance properties of the specified routing policy.  This analysis yields a lower  
bound on the number of link failures required to disconnect one abstract location from another. 
Any concrete instance of the abstract topology will adhere to the given fault tolerance property.

@@

\vspace{0.5em}
\noindent
\textbf{Contributions}: To summarize, our contributions are:
%
\begin{itemize}[noitemsep,nolistsep,label={\large\textbullet}]
\item New topology abstractions for network programming
based on graph homomorphisms and connectivity rules.
\item New algorithms for analyzing routing policy and fault tolerance over
abstract topologies.
\item Implementation and evaluation of a \sysname compiler that generates
BGP templates and is much faster
than compilers based on concrete topologies.
\end{itemize}

@@

All route announcements carry an {\em AS path}, the sequence of BGP networks, called autonomous systems (ASes), that will be traversed to reach the destination.
Optionally, they may also include one or more {\em communities}, which are arbitrary tags whose semantics are agreed upon out of band.

@@

To simplify them, operators are adopting a template-based approach~\cite{hatch,thwack}. Instead of authoring a configuration per router, operators author a template per role.
%
A {\em role} is a specific function that is served by one or more routers.
For example, the network in Figure~\ref{fig:example} might have five roles: spine, global aggregator, global ToR, local aggregator, and local ToR.
%
Figure~\ref{fig:templates} shows an example of what a small component of a template for the spine role in the two data centers might look like. The template has parameters for various aspects of the configuration (\EG, neighbor list, local prefixes) and is compiled to low-level device configurations by instantiating the parameters using the network topology and a database of network information.

@@

@@

@@

Our topology abstractions consist of several concepts.
The primary one is a role-based abstraction that allows an operator to map routers in the concrete network to roles in the abstract network. Figure~\ref{fig:example3} shows an example of this abstraction for both networks from \S\ref{sec:motivation}. In the example, the concrete networks are abstracted into a new topology with 5 different roles: local ToR (TL), global ToR (TG), local aggregator (AL), global aggregator (AG), and spine (S).

@@

On its own, this abstraction loses a lot of information about the concrete network's structure, making it difficult to reason precisely about fault-tolerance.
For example, with this abstraction any spine router may or may not connect to any aggregator router.
%
To capture concrete networks more precisely,
we introduce additional concepts. The first is topology hierarchy, captured by P and Q, which indicate that nodes in the ToR and aggregator roles are grouped into pods.
The second is node and edge \emph{multiplicity}. Each edge (and node) is labelled
with a symbolic variable (\EG, $e1$) that denotes a constraint on the number of edges (and nodes) that may appear in any valid concrete network. Operators can capture concrete network invariants by adding constraints on the symbolic variables using logical formulas.

@@

Our topology abstractions can also capture concrete topologies by using a one-to-one correspondence between abstract and concrete nodes/edges. This allows operators to define complex networks in which some (e.g., legacy) parts of the network cannot evolve while others can.

@@

Second, \sysname checks if the fault-tolerance policy can be met by considering the joint impact of the abstract topology and routing policy. Joint analysis is needed, because connectivity depends on both: traffic will not flow along valid topological paths if the routing policy disallows it.
%
We develop a sound analysis based on computing the minimum
number of edge-disjoint, policy-compliant paths between pairs of nodes
over abstract topologies. If this number is less
than the desired fault-tolerance level for a pair of nodes, \sysname declares that the
policy cannot be met.

@@

@@

We are now ready to generate the PG. Intuitively, the PG captures topology and routing constraints by ``intersecting" the finite automata associated with the policy regular expressions with the graph structure of the topology.
Because there can be a separate routing policy for each predicate $t$ in the policy, we construct one PG for each predicate.

@@

Figure~\ref{fig:example-compilation} shows the PG for the data center policy that applies to all external traffic ($\CD{\True \Path \Exit(N1~\Prefer~N2)}$).
%
The first automaton represents the more preferred constraint $\CD{\Exit(N1)}$ and the second automaton represents the less preferred constraint $\CD{\Exit(N2)}$. The PG is shown for both an instance of a simple concrete network matching the abstraction from \S\ref{sec:overview} as well as for the abstract topology.

@@

\begin{lem}
\label{lem:homomorphism}
If we have a graph homomorphism $f : G \rightarrow G^A$, concrete product graph $PG = (G',\mathit{start},\Pref)$ and abstract product graph $PG^A = (G'^A, \mathit{start}^A, \Pref^A)$, then there is a homomorphism $f_{pg} : G' \rightarrow G'^A$ where:
\[ \begin{array}{rcl}
  f_{pg}( \mathit{start} ) & = & \mathit{start}^A  \\
  f_{pg}( (l,q_1,\ldots,q_n) ) & = & (f(l),q_1,\ldots,q_n) \\
\end{array} \]
\end{lem}
%
As shown in \S\ref{sec:generation}, our generation strategy commutes with template instantiation, meaning that we obtain the same results if we instantiate the abstraction early, or if we defer the instantiation until after template generation.

@@

@@

We frame satisfying the fault-tolerance requirements as an analysis problem over the structure of the PG. In particular, we develop an analysis that uses information embedded in the abstract topology to infer bounds on the number of edge-disjoint paths between pairs of concrete nodes.

For each node in the abstract PG,
the idea is to infer facts learned about the number of edge-disjoint paths
to groups of concrete routers in the node's role.
More specifically, we maintain fact of the form:
%
\[ \begin{array}{c}
  L_{X_1}, \ldots, L_{X_n}(j,k)
\end{array} \]
\noindent
%
where each label $L \in \{S,A\}$ is either $S$, which stands for ``some" or is $A$, which stands for ``all". There is one label for each pod in the abstraction pod hierarchy under which the abstract node appears. For a given node, $L_{X_1}$ corresponds to the outermost pod, $L_{X_{n-1}}$ corresponds to the innermost pod, and $L_{X_n}$ to the node itself.
Semantically, $L_{X_1}, \ldots, L_{X_n}(j,k)$ means that starting from some concrete source node, for some/all pods $X_1, \ldots, X_{n-1}$
and for some/all groups of nodes in the role $X_n$ of size $j$,
there are $k$ paths to each such that all $j*k$ paths are edge-disjoint.

@@

Figure~\ref{fig:inference-rules} displays the collection of rules used to infer facts about disjoint paths.
Each rule is read from bottom to top. The label on the bottom left is a known fact. We use $L$ to represent a rule that is parametric over the label ($S$ or $A$). Labels on other nodes correspond to facts learned after applying the rule. The box shows the conditions that must be valid, given the abstraction constraints, for the rule to apply.

@@

The first rule, \infrule{I-out1} applies to a learned fact of the form $L_m(j,k)$ where the number of outgoing edges from any concrete node in the $m$ role is greater than 0. In the worst case, the largest group of concrete nodes we could hope to reach at the $n$ role would be $e_1$ since all j nodes at the bottom may have outgoing edges to the same concrete nodes at the top. Furthermore, the total number of disjoint paths to the $j$ nodes at the bottom is equal to $j*k$. Since extending the existing disjoint paths with disjoint edges keeps the paths disjoint, and since we cannot exceed the current number of disjoint paths to the concrete nodes in role $m$ on the bottom, the largest reachable group for the role $n$ on the top will be $min(j*k,e_1)$.
%
We conservatively use $1$ for the number of disjoint paths to each node in role $n$, since when $n$ is very large, all reachable nodes in role $m$ might only have a single edge to completely different nodes in $n$.

@@

@@

@@

@@

The algorithm could infer that there is at least 1 disjoint path to any spine router, and at least 2 disjoint paths to any TL router. In this case, the analysis is precise. There exists a concrete network, namely the data center from Figure~\ref{fig:example2}, where a single failure can disconnect a global ToR from a spine router due to the valley-free constraint.

@@

@@

For example, in Figure~\ref{fig:example-compilation} the inequality $(S1,0,1) \leq (S1,1,0)$ holds since nodes on the left side of the PG can always match transitions made on the right hand side with respect to the $\geq_{rank}$ relation. This relation does not hold the other way around since $(S1,0,1) \ngeq_{rank} (S1,1,0)$. Therefore, advertisements received at $S1$ with tag $(1,0)$ must be preferred to those received at $S1$ with tag $(0,1)$.
Notice that in the abstract PG $(S,0,1) \leq (S,1,0)$ also holds. This leads to the following observation:

@@

To prevent the non-local changes induced by template variables, we modify compilation in the following ways. First, we associate a new unique community tag for each template variable (\EG, {\small \$GP}), and add this tag where the route is originated (\EG, role TG). Then, template variable tests elsewhere in the policy are replaced with a new test on this tag. Finally, during template instantiation the tags are left unmodified.
Figure~\ref{fig:bgp-configs} (right) shows the spine and ToR templates after this transformation. Routers in the TG role will originate ($\{ \mathrm{start} \}$) global prefixes and tag them with a unique tag, while routers in the spine role match the tag.

@@

      Fat tree~\cite{fattree} & -- & \cmark & \cmark & \cmark & \cmark  \\ \hline
      Facebook~\cite{facebook-fattree} & -- & \cmark & \cmark & \cmark & \cmark \\ \hline
      F10~\cite{f10-fattree} & -- & \cmark & \cmark & \cmark & \cmark \\ \hline
      VL2~\cite{vl2-fattree} & -- & \cmark & \cmark & \cmark & \cmark \\ \hline

@@

@@

\para{Hypercube Topologies}
Hypercube variants can be used as an alternative to Clos-style topologies for networks with port density routers. The HyperX~\cite{hyperx} topology generalizes the hypercube and butterfly topologies and includes parameters $L$ for the lattice dimension of the network, and $S_i$ for the node multiplicity of each dimension $i$.
For a fixed number of dimensions $L$, we abstract each full mesh of $S_L$ nodes into its own abstract node. Nodes in dimension $S_{x-1}$ are abstracted using pods of abstract nodes from dimension $S_x$. Figure~\ref{fig:example-abstractions} shows an example for $L=2$.

\para{Results}
The bottom part of Figure~\ref{fig:analysis-precision} shows the results for all types of topologies coupled with shortest-path routing. (Valley-free routing is not meaningful for non-tree-based topologies.) For all tree-based topologies, the analysis is precise for determining reachability, but for three of them, it does not compute a tight bound for disjoint paths for all router pairs. Specifically, it underestimates ToR-to-spine paths; it fails to account for some circuitous paths that traverse another spine because it could not disambiguate two concrete spines that map to the same abstract role.
%
For instance, for the fat tree topology~\cite{fattree}, it only finds 1 path between any ToR and any Spine when there should always be at least two. However, in this case the analysis computes the correct worst case connectivity between any source ToR and any other destination aggregation or ToR router. A similar pattern occurs with other tree-based topologies.
For both recursive topologies, the analysis can only accurately determine reachability.
